Influence of Connectivity on Dung Beetle Communities

### 2025-05-22 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
hill numbers

@@

>>>>

hill numbers are a set of biodiversity metrics designed to quantify biodiversity and richness differently depending on how we want to emphasize abundance while also accounting for differences in sampling sizes and efforts (read more about this Eric)

@@

- Chao et al. 2014 -> incorporating abundance into calculating diversity metrics is important for studying functionality in particular since some species that may not be as abundant as others may not contribute to an ecosystem function as much as others.

- ^ At the same time rare species may be filling a specific niche or we might be concerned about exotics or at risk species.
